---
title: ""
subtitle: ""
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: ""
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

```{r}
#| message: false
#| echo: false

# load packages
packages <- c("tidyverse", "boot", "broom.mixed", "collapse", "dataverse", "gutenbergr", "janitor", "knitr", "marginaleffects", "modelsummary", "rstanarm", "tidybayes", "loo")

# Function to check and install missing packages
install_and_load <- function(packages) {
  for (package in packages) {
    if (!require(package, character.only = TRUE)) {
      install.packages(package)
      library(package, character.only = TRUE)
    }
  }
}

# Call the function with the list of packages
install_and_load(packages)
```

```{r}
#| message: false
#| echo: false

# read in data
file_path_0 <- "../../inputs/data/raw_data.csv"
file_path_1 <- "../../outputs/data/cleaned_data.csv"
file_path_2 <- "../../outputs/data/top_5_cause_data.csv"
file_path_3 <- "../../outputs/data/summarized_top_5_cause_data.csv"

raw_data <- read_csv(file_path_0, show_col_types = FALSE)
cleaned_data <- read_csv(file_path_1, show_col_types = FALSE)
top_5_cause_data <- read_csv(file_path_2, show_col_types = FALSE)
summarized_top_5_cause_data <- read_csv(file_path_3, show_col_types = FALSE)
```

# Introduction



# Data {#sec-data}

Data used in this paper was cleaned, processed and tested with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `tidybayes` [@citeTidybayes], `loo` [@citeLoo], `testthat` [@citeTestthat].

## Source



## Method

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-causes
#| tbl-cap: top 8 major causes in 2019



```



# Results {#sec-res}

```{r}
#| include: false



```

## Data Trend

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-trends-1
#| fig-cap: Trend for Alberta Mortality-Top 5 Causes



```

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-trends-2
#| fig-cap: Trend for Alberta Mortality-Sum of Causes



```



## Modeling

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-summary
#| tbl-cap: summary of modeling



```



```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-models
#| fig-cap: Model Results
#| fig-subcap: ["Poisson Model","Negative Binomial Model"]
#| layout-ncol: 2
#| layout-nrow: 1



```



```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-cross_validation
#| tbl-cap: cross validation of modeling



```

# Discussion {#sec-dis}



## Demographic Shifts



## Health-related Behaviors



## Government Policies



## Environmental Changes



## Possible Improvements



# Conclusion {#sec-con}



\newpage




\newpage


# References


